SPEI_longterm

### 2018-02-12 analysis/drought/explore_spei_longterm.Rmd
include spei severe droughts and resilience trends

---
title: "SPEI_longterm"
author: "Antonio J. Perez-Luque"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

@@

```{r}
sev12 <- sev %>% filter(variable == "spei12") %>% arrange(desc(d_duration)) %>% 
  dplyr::select(-index_events, -cat, -decade, -variable)

pander(sev12)

```

>>>>

---
title: "SPEI_longterm"
author: "Antonio J. Perez-Luque"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

@@

```{r}
sev12 <- sev %>% filter(variable == "spei12") %>% arrange(desc(d_duration)) %>% 
  dplyr::select(-index_events, -decade, -variable)

write.csv(sev12, file=here::here('data/sequias', 'severe_spei12.csv'), row.names=FALSE)

pander(sev12)
```
